Finding Maximum $k$-Cliques Faster using Lazy Global Domination

### 2016-03-29 paper/paper.tex
Some more

\def\year{2016}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai16}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\usepackage{cleveref}
\usepackage{complexity}
\usepackage[ruled,vlined]{algorithm2e} % algorithms
\usepackage{longtable}
\usepackage{booktabs}                  % less ugly tables
\usepackage{tikz}                      % For pretty pictures
\usepackage{afterpage}
\usepackage{siunitx}
\usepackage{tikz}                      % For pretty pictures
\usepackage{gnuplot-lua-tikz}          % graphs

@@

\crefname{algocf}{algorithm}{algorithm}
\Crefname{algocf}{Algorithm}{Algorithms}

@@

@@

\begin{algorithm}\DontPrintSemicolon
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (cvrej1c) at ($(pic cs:cvrej1) + (0, 0.15)$);
        \coordinate (cvrej2c) at ($(pic cs:cvrej2) + (0, 0.00)$);
        \node [fill=safelightblue, rounded corners, fit=(cvrej1c) (cvrej2c)] { };

@@

    \nl $\FuncSty{maxKClique}$ :: (Graph $G$, Integer $k$) $\rightarrow$ Vertex Set \;
    \nl \Begin{
        \nl $G$ $\gets$ $G^k$ \mclabel{power} \;
        \nl permute $G$ so that vertices are in non-increasing degree order \mclabel{permute} \;
        \nl $\KwSty{global}$ $\Cbest$ $\gets$ $\emptyset$ \mclabel{cbest} \;
        \nl $\expand$($\emptyset$, $\vertexset(G)$) \mclabel{c} \mclabel{p} \;
        \nl $\KwSty{return}$ $\Cbest$ (unpermuted) \;
    }
    \;

    \nl $\expand$ :: (Vertex Set $C$, Vertex Set $P$) \;
    \nl \Begin{
        \nl ($\order$, $\bounds$) $\gets$ $\colourOrder$($P$) \mclabel{colouring} \;
        \nl \tikzmark{cvrej1}$\vrej$ $\gets$ $\kwunset$ \tikzmark{cvrej2} \;
        \nl \For{$i$ $\gets$ $|P|$ $\KwSty{downto}$ 1\mclabel{righttoleft}}{
            \nl \lIf{\textnormal{$|C|$ + $\bounds[i]$ $\le$ $|\Cbest|$}\mclabel{bound}}{$\KwSty{return}$}
            \nl \tikzmark{cdom1}\If{\textnormal{$\vrej$ $\ne$ $\kwunset$}}{
                \nl $P$ $\gets$ $P$ $\setminus$ $\dominated(\vrej)$ \tikzmark{cdom2} \mclabel{dominated} \;
            }
            \nl $v$ $\gets$ $\order[i]$ \mclabel{v} \;
            \nl \tikzmark{cvinp1}\If{$v$ $\in$ $P$\tikzmark{cvinp2}\mclabel{alreadyrejected}}{
                \nl $C$ $\gets$ $C + v$ \mclabel{vinstart} \;
                \nl \lIf{\textnormal{$|C| > |\Cbest|$}}{$\Cbest$ $\gets$ $C$\mclabel{unseat}}
                \nl $P'$ $\gets$ $P$ $\cap$ $\neighbourhood_G(v)$ \mclabel{pprime} \;
                \nl \lIf{$P'$ $\ne$ $\emptyset$}{$\expand$($C$, $P'$)\mclabel{vinend}\mclabel{recurse}}
                \nl \tikzmark{creject1}$C$ $\gets$ $C - v$ \mclabel{vnotinstart} \;
                \nl $P$ $\gets$ $P - v$\tikzmark{creject2} \mclabel{vnotinend} \;
            }
            \nl \tikzmark{cvrejg1}$\vrej$ $\gets$ $v$ \tikzmark{cvrejg2} \mclabel{vrej} \;
        }
    }
    \;

    \nl $\colourOrder$ :: (Vertex Set $P$) $\rightarrow$ (Vertex Array, Int Array) \;
    \nl \Begin{
        \nl ($\order$, $\bounds$) $\gets$ ($[]$, $[]$) \;
        \nl $\uncoloured$ $\gets$ $P$ \;
        \nl $\colour$ $\gets$ $1$ \mclabel{colour1} \;
        \nl \While{$\uncoloured$ $\ne$ $\emptyset$\mclabel{uncoloured}}{
            \nl $\colourable$ $\gets$ $\uncoloured$ \mclabel{currentcolourstart} \;
            \nl \While{$\colourable$ $\ne$ $\emptyset$}{
                \nl $v$ $\gets$ the first vertex of $\colourable$ \;
                \nl append $v$ to $\order$ \;
                \nl append $\colour$ to $\bounds$ \;
                \nl $\uncoloured$ $\gets$ $\uncoloured - v$ \;
                \nl $\colourable$ $\gets$ $\colourable \setminus \neighbourhood_G(v)$ \mclabel{currentcolourend}\mclabel{notcolourable}\;
            }
            \nl $\colour$ $\gets$ $\colour + 1$ \mclabel{colourplus1}
        }
        \nl $\KwSty{return}$ ($\order$, $\bounds$) \;
    }
    \;

@@

We may now describe the main recursive part of the algorithm. If $v$ is a vertex, then a clique in
$G^k$ either contains only $v$ and vertices adjacent to $v$, or does not contain $v$. This allows us
to grow cliques by repeatedly picking a vertex, and branching upon whether or not to include it. Our
growing clique is stored in the variable $C$, which is initially empty (\mcline{c}). We also track
which vertices may still be added to $C$ in the variable $P$, which initially contains every vertex
(\mcline{p}). The $\expand$ procedure picks a vertex $v$ (\mcline{v}), then considers adding $v$ to
$C$ (\mclinerange{vinstart}{vinend}): we create a new $P'$ from $P$ (\mcline{pprime}) by
rejecting vertices which are not adjacent to $v$ (and thus every vertex in $P'$ is adjacent to
\emph{every} vertex in $C$). If vertices remain in $P'$, we recurse (\mcline{recurse}). We then take
the opposite branch choice, and consider rejecting from $P$ and $C$
(\mclinerange{vnotinstart}{vnotinend}). We then loop, and pick a new $v$.

@@

Suppose a graph does contain one or more pairs of dominating vertices. We could make use of this
fact during search in at least two ways. Firstly, when accepting a vertex $w$, we may also
unconditionally accept any vertex $v$ which dominates $w$. Secondly, when rejecting a vertex $v$, we
may also unconditionally reject any vertex $w$ which is dominated by $v$.  We could also choose to
calculate domination globally (i.e.\ with respect to $G^k$, or even the original $G$), or locally
(i.e.\ with respect to the subgraph of $G^k$ induced by $C \cup P$).

@@

The lines marked in blue in \cref{algorithm:maxKClique} show how this is done. When a vertex $\vrej$
is rejected, we remove from $P$ any vertex that is dominated (with respect to $G^k$) by $\vrej$.
This is \mcline{dominated}; the set of dominated vertices calculated here should be cached.  One
might expect that this calculation would appear after \mcline{vnotinend}. However, this introduces a
cost if the bound allows the next choice of $v$ to be eliminated. Thus we simply remember that we
have rejected $v$ by storing it in $\vrej$ (\mcline{vrej}), and lazily postpone the filtering until
after the bound has been checked.

@@

\afterpage{
    {
    \onecolumn
\setlength{\LTcapwidth}{\textwidth}
\centering
\begin{longtable}{l c r rrr rrr}
    \caption{Experimental results for a range of graphs. For each graph, we consider $k$ equal to 2,
        3 and 4. In each case we show the density of $G^k$, and then for both the unmodified
        algorithm and the algorithm with our lazy global domination step, we give the size of a
        maximum $k$-clique, the number of nodes required, and the runtime in seconds. Some results
        were aborted after one day.}
    \label{table:results}
    \\

    \toprule

    & & & \multicolumn{3}{c}{Unmodified} & \multicolumn{3}{c}{With Domination} \\
    \cmidrule(lr){4-6}
    \cmidrule(lr){7-9}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} &
    \multicolumn{1}{c}{$\tilde{\omega}_k$} & \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{$\tilde{\omega}_k$} & \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule

    \endfirsthead

    \caption[]{(continued from previous page)} \\
    \toprule

    & & & \multicolumn{3}{c}{Unmodified} & \multicolumn{3}{c}{With Domination} \\
    \cmidrule(lr){4-6}
    \cmidrule(lr){7-9}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} &
    \multicolumn{1}{c}{$\tilde{\omega}_k$} & \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{$\tilde{\omega}_k$} & \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule

    \endhead

    \midrule
    \endfoot

    \bottomrule
    \endlastfoot

    \inputhaxx{gen-table-erdos}
    \midrule
    \inputhaxx{gen-table-dimacs}
    \midrule
    \inputhaxx{gen-table-dimacs10walshaw}
    \midrule
    \inputhaxx{gen-table-dimacs10cluster}
\end{longtable}}\twocolumn}

@@

In the first part of \cref{table:results} we present experimental results from Erd\H{o}s
collaboration graphs from the Pajek dataset by Vladimir Batagelj and Andrej
Mrvar\footnote{\texttt{http://vlado.fmf.uni-lj.si/pub/networks/data/}}.  We were able to solve all of
these problems in under eight minutes (and all but three in under two seconds) when using the
domination rule. However, using the unmodified maximum clique algorithm, two of these results did
not finish running within one day. Note that for $k = 4$, a $k$-clique covers all of ``Erdos02''.

@@

In the second part of \cref{table:results} we present results from the ``clique'' graphs from the
Second DIMACS implementation challenge\footnote{\texttt{http://dimacs.rutgers.edu/Challenges/}}. These
graphs were designed to test maximum clique implementations. Nearly all of these graphs have
diameter 2, so a 2-clique covers the entire graph---we have ignored these. The only exceptions are
the ``c-fat'' family (all of which are trivial for a maximum clique solver), and one of the
``p\_hat'' graphs.

@@

The third part of \cref{table:results} presents results from the smallest 20 partitioning graphs
from the 10th DIMACS Implementation
Challenge\footnote{\texttt{http://staffweb.cms.gre.ac.uk/~wc06/partition/}}.  Many of these graphs are
considerably larger than those typically considered for the maximum clique problem, and we might
expect our $O(|V|^2)$ memory requirements to cause problems. Nonetheless, with the domination rule
there is only one instance which we were unable to solve within a day (and without the domination
rule, there are two).

@@

The final part of \cref{table:results} presents results from the smallest 20 partitioning graphs
from the 10th DIMACS Implementation
Challenge\footnote{\texttt{http://www.cc.gatech.edu/dimacs10/archive/clustering.shtml}}. Again, from a
maximum clique perspective these would be considered unusually large graphs. However, only five were
unsolvable within a day (plus a sixth when the domination rule was not used), and half of the
problems took under two seconds.

>>>>

% vim: set spell spelllang=en tw=100 et sw=4 sts=4 :

\def\year{2016}\relax
\documentclass[letterpaper]{article}
\usepackage{aaai16}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\usepackage{cleveref}
\usepackage{complexity}
\usepackage[ruled,vlined]{algorithm2e} % algorithms
\usepackage{booktabs}                  % less ugly tables
\usepackage{tikz}                      % For pretty pictures
\usepackage{afterpage}
\usepackage[tight-spacing=true]{siunitx}
\usepackage{tikz}                      % For pretty pictures
\usepackage{gnuplot-lua-tikz}          % graphs

@@

% cref style
\crefname{algocf}{algorithm}{algorithm}
\Crefname{algocf}{Algorithm}{Algorithms}
\crefname{figure}{figure}{figures}
\Crefname{figure}{Figure}{Figures}
\crefname{table}{table}{tables}
\Crefname{table}{Table}{Tables}

@@

\renewcommand{\topfraction}{0.9}
\renewcommand{\bottomfraction}{0.8}
\renewcommand{\dbltopfraction}{0.9}
\renewcommand{\textfraction}{0.05}
\setcounter{dbltopnumber}{2}
\renewcommand{\floatpagefraction}{0.85}
\renewcommand{\dblfloatpagefraction}{0.85}

@@

\begin{algorithm}[t]\DontPrintSemicolon
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (cvrej1c) at ($(pic cs:cvrej1) + (0, 0.15)$);
        \coordinate (cvrej2c) at ($(pic cs:cvrej2) + (0, 0.00)$);
        \node [fill=safelightblue, rounded corners, fit=(cvrej1c) (cvrej2c)] { };

@@

    \nl $\FuncSty{maxKClique}$ :: (Graph $G$, Integer $k$) $\rightarrow$ Vertex Set \;
    \nl \Begin{
        \nl $G$ $\gets$ $G^k$ \mclabel{power} \;
        \nl permute $G$ into non-increasing degree order \mclabel{permute} \;
        \nl $\KwSty{global}$ $\Cbest$ $\gets$ $\emptyset$ \mclabel{cbest} \;
        \nl $\expand$($\emptyset$, $\vertexset(G)$) \mclabel{c} \mclabel{p} \;
        \nl $\KwSty{return}$ $\Cbest$ (unpermuted) \;
    }
    \vspace{0.5ex}

    \nl $\expand$ :: (Vertex Set $C$, Vertex Set $P$) \;
    \nl \Begin{
        \nl ($\order$, $\bounds$) $\gets$ $\colourOrder$($P$) \mclabel{colouring} \;
        \nl \tikzmark{cvrej1}$\vrej$ $\gets$ $\kwunset$ \tikzmark{cvrej2} \;
        \nl \For{$i$ $\gets$ $|P|$ $\KwSty{downto}$ 1\mclabel{righttoleft}}{
            \nl \lIf{\textnormal{$|C|$ + $\bounds[i]$ $\le$ $|\Cbest|$}\mclabel{bound}}{$\KwSty{return}$}
            \nl \tikzmark{cdom1}\If{\textnormal{$\vrej$ $\ne$ $\kwunset$}}{
                \nl $P$ $\gets$ $P$ $\setminus$ $\dominated(\vrej)$ \tikzmark{cdom2} \mclabel{dominated} \;
            }
            \nl $v$ $\gets$ $\order[i]$ \mclabel{v} \;
            \nl \tikzmark{cvinp1}\If{$v$ $\in$ $P$\tikzmark{cvinp2}\mclabel{alreadyrejected}}{
                \nl $C'$ $\gets$ $C + v$ \mclabel{vinstart} \;
                \nl \lIf{\textnormal{$|C'| > |\Cbest|$}}{$\Cbest$ $\gets$ $C'$\mclabel{unseat}}
                \nl $P'$ $\gets$ $P$ $\cap$ $\neighbourhood_G(v)$ \mclabel{pprime} \;
                \nl \lIf{$P'$ $\ne$ $\emptyset$}{$\expand$($C'$, $P'$)\mclabel{vinend}\mclabel{recurse}}
                \nl $P$ $\gets$ $P - v$\tikzmark{creject2} \mclabel{vnotin} \;
            }
            \nl \tikzmark{cvrejg1}$\vrej$ $\gets$ $v$ \tikzmark{cvrejg2} \mclabel{vrej} \;
        }
    }
    \vspace{0.5ex}

    \nl $\colourOrder$ :: (Vertex Set $P$) $\rightarrow$ (Vertex Array, Int Array) \;
    \nl \Begin{
        \nl ($\order$, $\bounds$) $\gets$ ($[]$, $[]$) \;
        \nl $\uncoloured$ $\gets$ $P$ \;
        \nl $\colour$ $\gets$ $1$ \mclabel{colour1} \;
        \nl \While{$\uncoloured$ $\ne$ $\emptyset$\mclabel{uncoloured}}{
            \nl $\colourable$ $\gets$ $\uncoloured$ \mclabel{currentcolourstart} \;
            \nl \While{$\colourable$ $\ne$ $\emptyset$}{
                \nl $v$ $\gets$ the first vertex of $\colourable$ \;
                \nl append $v$ to $\order$ \;
                \nl append $\colour$ to $\bounds$ \;
                \nl $\uncoloured$ $\gets$ $\uncoloured - v$ \;
                \nl $\colourable$ $\gets$ $\colourable \setminus \neighbourhood_G(v)$ \mclabel{currentcolourend}\mclabel{notcolourable}\;
            }
            \nl $\colour$ $\gets$ $\colour + 1$ \mclabel{colourplus1}
        }
        \nl $\KwSty{return}$ ($\order$, $\bounds$) \;
    }
    \vspace{0.5ex}

@@

We may now describe the main recursive part of the algorithm. If $v$ is a vertex, then a clique in
$G^k$ either contains only $v$ and vertices adjacent to $v$, or does not contain $v$. This allows us
to grow cliques by repeatedly picking a vertex, and branching upon whether or not to include it. Our
growing clique is stored in the variable $C$, which is initially empty (\mcline{c}). We also track
which vertices may still be added to $C$ in the variable $P$, which initially contains every vertex
(\mcline{p}). The $\expand$ procedure picks a vertex $v$ (\mcline{v}), then considers adding $v$ to
$C$ (\mclinerange{vinstart}{vinend}): we create a new $P'$ from $P$ (\mcline{pprime}) by
rejecting vertices which are not adjacent to $v$ (and thus every vertex in $P'$ is adjacent to
\emph{every} vertex in $C$). If vertices remain in $P'$, we recurse (\mcline{recurse}). We then take
the opposite branch choice, and consider rejecting from $P$ and $C$
(\mcline{vnotin}). We then loop, and pick a new $v$.

@@

Suppose a graph does contain one or more pairs of dominating vertices. We could make use of this
fact during search in at least two ways. Firstly, when accepting a vertex $w$, we may also
unconditionally accept any vertex $v$ which both dominates and is adjacent to $w$. Secondly, when
rejecting a vertex $v$, we may also unconditionally reject any vertex $w$ which is dominated by $v$.
We could also choose to calculate domination globally (i.e.\ with respect to $G^k$, or even the
original $G$), or locally (i.e.\ with respect to the subgraph of $G^k$ induced by $C \cup P$).

@@

The lines marked in blue in \cref{algorithm:maxKClique} show how this is done. When a vertex $\vrej$
is rejected, we remove from $P$ any vertex that is dominated (with respect to $G^k$) by $\vrej$.
This is \mcline{dominated}; the set of dominated vertices calculated here should be cached.  One
might expect that this calculation would appear after \mcline{vnotin}. However, this introduces a
cost if the bound allows the next choice of $v$ to be eliminated. Thus we simply remember that we
have rejected $v$ by storing it in $\vrej$ (\mcline{vrej}), and lazily postpone the filtering until
after the bound has been checked.

@@

@@

In \cref{table:erdos} we present experimental results from Erd\H{o}s
collaboration graphs from the Pajek dataset by Vladimir Batagelj and Andrej
Mrvar\footnote{http://vlado.fmf.uni-lj.si/pub/networks/data/}.  We were able to solve all of
these problems in under eight minutes (and all but three in under two seconds) when using the
domination rule. However, using the unmodified maximum clique algorithm, two of these results did
not finish running within one day. Note that for $k = 4$, a $k$-clique covers all of ``Erdos02''.

\begin{table}
    \tiny
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
    \inputhaxx{gen-table-erdos}
    \bottomrule
\end{tabular}
\caption{Experimental results for Erd\H{o}s collaboration graphs. For each
graph, we consider $k$ equal to 2, 3 and 4. In each case we show the density of
$G^k$, the size of a maximum $k$-clique, and then for both the unmodified
algorithm and the algorithm with our lazy global domination step, the number of
nodes required, and the runtime in seconds.}\label{table:erdos}
\end{table}

@@

In \cref{table:clique} we present results from the ``clique'' graphs from the
Second DIMACS implementation challenge\footnote{http://dimacs.rutgers.edu/Challenges/}. These
graphs were designed to test maximum clique implementations. Nearly all of these graphs have
diameter 2, so a 2-clique covers the entire graph---we have ignored these. The only exceptions are
the ``c-fat'' family (all of which are trivial for a maximum clique solver), and one of the
``p\_hat'' graphs.

\begin{table}
    \tiny
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
    \inputhaxx{gen-table-dimacs}
    \bottomrule
\end{tabular}
\caption{Experimental results for DIMACS clique graphs with diameter greater
    than two. For each graph, we consider $k$ equal to 2, 3 and 4. In each case
    we show the density of $G^k$, the size of a maximum $k$-clique, and then
    for both the unmodified algorithm and the algorithm with our lazy global
domination step, the number of nodes required, and the runtime in seconds.}\label{table:clique}
\end{table}

@@

\Cref{table:partitioning} presents results from the smallest 20 partitioning graphs
from the 10th DIMACS Implementation
Challenge\footnote{http://staffweb.cms.gre.ac.uk/\textasciitilde{}wc06/partition/}.  Many of these graphs are
considerably larger than those typically considered for the maximum clique problem, and we might
expect our $O(|V|^2)$ memory requirements to cause problems. Nonetheless, with the domination rule
there is only one instance which we were unable to solve within a day (and without the domination
rule, there are two).

\begin{table}
    \tiny\setlength{\tabcolsep}{4pt}
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
    \inputhaxx{gen-table-dimacs10walshaw}
    \bottomrule
\end{tabular}
\caption{Experimental results for the smaller DIMACS partitioning graphs. For
    each graph, we consider $k$ equal to 2, 3 and 4. In each case we show the
    density of $G^k$, the size of a maximum $k$-clique, and then for both the
    unmodified algorithm and the algorithm with our lazy global domination
step, the number of nodes required, and the runtime in seconds.}\label{table:partitioning}
\end{table}

@@

\Cref{table:clustering} presents results from the smallest 20 clustering graphs
from the 10th DIMACS Implementation
Challenge\footnote{http://www.cc.gatech.edu/dimacs10/archive/clustering.shtml}. Again, from a
maximum clique perspective these would be considered unusually large graphs. However, only five were
unsolvable within a day (plus a sixth when the domination rule was not used), and half of the
problems took under two seconds.

\begin{table}
    \tiny\setlength{\tabcolsep}{4pt}
    \begin{tabular}{l c rr rr rr}
        \toprule
        & & & & \multicolumn{2}{c}{Unmodified} & \multicolumn{2}{c}{With Domination} \\
    \cmidrule(lr){5-6}
    \cmidrule(lr){7-8}
    Instance & \multicolumn{1}{c}{$k$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{$\tilde{\omega}_k$} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} &
    \multicolumn{1}{c}{Nodes} & \multicolumn{1}{c}{Time} \\
    \midrule
    \inputhaxx{gen-table-dimacs10cluster}
    \bottomrule
\end{tabular}
\caption{Experimental results for the smaller DIMACS clustering graphs. For
    each graph, we consider $k$ equal to 2, 3 and 4. In each case we show the
    density of $G^k$, the size of a maximum $k$-clique, and then for both the
    unmodified algorithm and the algorithm with our lazy global domination
step, the number of nodes required, and the runtime in seconds.}\label{table:clustering}
\end{table}
